---
title: "Assignment 8"
author: "Kyle Walker"
date: "11/4/2019"
output: html_document
---
```{r}
library(readr)
library(tidyverse)
library(ggplot2)
titanic <- as.data.frame(read_csv(file = "C:/Users/student/Documents/Senior Year/MATH 421/titanic.csv"))
```

### 1. Working with the Titanic dataset. Use the map function to compute the number of NA for each columns. Use map_int to turn the output to an interger vector.

```{r}
map_int(titanic, ~sum(is.na(.)))
```

### 2. Use map function to calculate the mean of numeric variables in the Titanic dataset.
```{r}
titanic %>% 
  select_if(is.numeric) %>% 
    map(~mean(., na.rm = T))
```

### 3. . Use map function to show the means, medians, and standard deviations of numeric variables in the Titanic dataset. Use map_df to show the result in a data frame format.
```{r}
titanic %>% 
  select_if(is.numeric) %>% 
    map_df(function(x) {
      stats <- array(c(mean(x, na.rm = T), median(x, na.rm = T), sd(x, na.rm = T)), dim= 3)
      return(stats)
      }
    )
```

### 4. Use map function to show the mode (most frequent category) and the number of categories for each categorical variables. Put the result in data frame.
```{r}
titanic %>% 
  select_if(is.character) %>% 
    map_df(function(x) {
      ux <- unique(x)
      tab <- tabulate(match(x, ux))
      categ <- array(c(sample(as.character(x[tab == max(tab)]),1), length(table(x))))
      return(categ)
    })
```

### 5. Use map to graph the histograms of numeric variables and bar charts of categorical variables in the Titanic data

```{r warning=FALSE}
tn <- titanic %>% 
  select_if(is.numeric)
    map(1:length(tn), function(x) {
      ggplot(,aes(tn[[x]])) +
        geom_histogram() +
        labs(x= colnames(tn[x])) 
      }
    )
    
tc <- titanic %>% 
  select_if(is.character)
map(1:length(tc), function(x) {
  ggplot(,aes(tc[[x]])) +
    geom_bar() +
    labs(x=colnames(tc[x]))
})
```

### 6. Redo Question 11 in Assignment 7 using map. 
```{r warning=FALSE}
k_map <- function(d, k) {
  if(k == 1) {
    d <- d %>% 
      select_if(is.character) %>% 
        select_if(~length(table(.)) < 4)
    
    map(1:length(d), function(x)
      {map(1:length(d), function(y) {
          print(ggplot(d, aes(x=d[[x]], fill=d[[y]])) +
                  geom_bar() +
                  labs(x = colnames(d[x]),
                       fill= colnames(d[y])))
            }
          )
        }
      )
  }
  if(k==2) {
    d <- d %>% 
      select_if(is.numeric)
    map(1:length(d), function(x) {
      ggplot(d, aes(x=d[[x]])) +
            geom_density() +
            labs(x=colnames(d[x])
            )
    })
  }
  if(k == 3) {
    dc <- d %>% 
      select_if(is.character) %>% 
        select_if(~length(table(.)) < 4)
    dn <- d %>% 
      select_if(is.numeric)
    map(1:length(dn), function(x){
      map(1:length(dc), function(y){
        ggplot(, aes(x=dn[[x]], color= dc[[y]]))+
          geom_density()+
          labs(y= 'Density',
               x=colnames(dn[x]),
               color= colnames(dc[y]))
      })
    })
  }
}
k_map(titanic, 3)
```



### 7. Write a function, using map, to
#### • input: a data frame
#### • output: a data frame of consist three columns x1, x2 and r where the pairs (x1, x2) are all possible pairs of continuous variables of the input data frame and r is the corresponding r square of x1 and x2.
#### Test the function on the titanic data assuming that the PassengerID is also a coninuous variable.

```{r warning=FALSE}
#df <- data.frame()
r_square <- function(d) {
  dn <- d %>% 
    select_if(is.numeric)
  #df <- data.frame(matrix(c("x1","x2", 1), nrow= 0, ncol=3))
  #names(df) <- c('x1', 'x2', 'r')
  map_df(1:length(dn), function(x) {
    map_df(1:length(dn), function(y) {
      r <- as.numeric(summary(lm(dn[[x]]~dn[[y]], dn))$r.square)
      #values <- c(colnames(dn[x]), colnames(dn[y]), as.numeric(r))
      data.frame(colnames(dn[x]), colnames(dn[y]), round(as.numeric(r),3))
      #print(values)
      #df <- rbind(df, values)
      #return(df)
    })
  })
  #return(df)
}
r_square(titanic)
#df
```

